---
title: "TANGO-CC: An open-source website for researchers to build a culture-sensitive task of gaze understanding"
shorttitle: "measuring gaze understanding across the globe"
author: 
  
  - name          : "Julia Christin Prein"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Max Planck Institute for Evolutionary Anthropology, Deutscher Platz 6, 04103 Leipzig, Germany"
    email         : "julia_prein@eva.mpg.de"
    role          :
      - Conceptualization
      - Methodology
      - Software
      - Investigation
      - Formal Analysis
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
      
  - name          : "Daniel B. M. Haun"
    affiliation   : "1"
    role          :
      - Supervision
      - Writing - Review & Editing
      
  - name          : "Manuel Bohn"
    affiliation   : "1,2"
    role          :
      - Conceptualization
      - Writing - Review & Editing
    
affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "2"
    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"
abstract: |
  
keywords          : "cross-cultural psychology, social-cognitive development, gaze following, individual differences, reliability"
wordcount         : "XXX"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : yes 
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes   :
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
editor_options    : 
  markdown: 
    wrap: sentence
bibliography      : "../../references.bib"
---

```{r setup, include = FALSE}
library("tidyverse")
library("papaja")
library("kableExtra")
library("brms")
library("janitor")

theme_set(theme_classic())
```

```{r analysis_preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction
- increased interest in cc research but not many new methods that enable or ease cross cultural research
- hard to capture ind diff, even harder in cc settings
- goal: comparable data across cultural settings
- approach 1: standardized procedure, as similar as possible. taken here
- approach 2: see in each cultural setting how to translate the psychological construct into experiment
- prein2023tango: works for ind diff. reliable. 
- supplements prein2023variation: differences between animal & human faces

# Methods
- testing setups: rural & urban
- no prior touchscreen experience needed
- how does website work: which variables you can select
- output from website
- shiny app?!
- psychometric properties of tango germany
- describe cc sample

# Results
- splithalf per cultural setting
- effect of age distribution, different for each cultural setting
- in plot: weigh sample size: x: splithalf, y: culture, size geom count: sample size
- visualize ind diff
- plot training trials argument for children understand to touch balloon
- response time?
- droup outs across cultures

# Discussion
- flexibility for researchers
- adjust to each cultural setting: faces, languages, background scene
- easy to add new layers to svg to adjust even further
- minimal language demands
- worked across 16(?) different communities already

# Limitations
- measure same construct across communities?
- technology effects

# Conclusion

\newpage

# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```
